### 2017-10-16 PVDR/WaterlooMidnightSun_ASC2018PVDR.tex
work in progress

\section{Mechanical}
\subsection{Contacts}
Questions regarding the mechanical design and implementation of MSXII should be directed to one of the following contacts:

\begin{table}[!h]
\centering
\begin{tabular}{llll}
\toprule
Name            & Title               & Phone        & Email \\
\midrule        
Tak Alguire     & Project Manager     & 519-574-4610 & tak.alguire@uwmidsun.com \\
Minghao Ji      & Engineering Manager & 519-500-1292 & minghao.ji@uwmidsun.com \\
Devon Copeland  & Mechanical Lead     & 226-792-7383 & devon.copeland@uwmidsun.com \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Overview}
MSXII is a dual-occupant Cruiser class vehicle. Its structural design uses a steel alloy tube chassis with non-structural fibreglass body panels. The majority of the vehicle's powertrain systems are located behind the occupant cell, including the battery pack, power junction box, motor controllers, and EV charger. The vehicle is rear-wheel driven by two hub-mounted DC motors. The locations of these components are marked in Figure \ref{fig:msxii-top-view} and Figure \ref{fig:msxii-side-view}. Major vehicle dimensions are summarized in Table \ref{tab:msxii-dimensions}.

\begin{figure}
\centering
%\includegraphics{figures/msxii-top-view}
\caption{Top view showing major dimensions and system positions}
\label{fig:msxii-top-view}
\end{figure}

\begin{figure}
\centering
%\includegraphics{figures/msxii-side-view}
\caption{Side view showing major dimensions and system positions}
\label{fig:msxii-side-view}
\end{figure}

\begin{table}
\centering
\begin{tabular}{cc}
\toprule
Parameter & Value \\
\midrule
Wheelbase    & \SI{2.60}{\metre} \\
Track        & \SI{1.60}{\metre} \\
Total length & TODO              \\
Total width  & TODO              \\
Height       & TODO              \\
\bottomrule
\end{tabular}
\caption{Table of major vehicle dimensions}
\label{tab:msxii-dimensions}
\end{table}

@@

\begin{figure}
\centering
%\includegraphics{figures/chassis-front}
\caption{Chassis, front view}
\label{fig:chassis-front}
\end{figure}
\begin{figure}
\centering
%\includegraphics{figures/chassis-top}
\caption{Chassis, top view}
\label{fig:chassis-top}
\end{figure}
\begin{figure}
\centering
%\includegraphics{figures/chassis-side}
\caption{Chassis, side view}
\label{fig:chassis-side}
\end{figure}

@@

\begin{figure}
\centering
%\includegraphics{figures/welding-jig}
\caption{Welding jig under construction}
\label{fig:welding-jig}
\end{figure}

@@

\begin{figure}
\centering
%\includegraphics{figures/roll-cage}
\caption{Chassis with roll cage elements highlighted}
\label{fig:roll-cage}
\end{figure}

@@

\begin{figure}
\centering
%\includegraphics{figures/seat-belt-tab-positions}
\caption{Chassis mounting points for seat belts}
\label{fig:seat-belt-tab-positions}
\end{figure}

\begin{figure}
\centering
%\includegraphics{figures/seat-belt-tab}
\caption{Single seat belt tab}
\label{fig:seat-belt-tab}
\end{figure}

\begin{figure}
\centering
%\includegraphics{figures/seat-belt-side-view}
\caption{Side view of seat belt geometry}
\label{fig:seat-belt-side-view}
\end{figure}

\begin{figure}
\centering
%\includegraphics{figures/seat-belt-top-view}
\caption{Top view of seat belt geometry}
\label{fig:seat-belt-top-view}
\end{figure}

@@

\begin{figure}
\centering
%\includegraphics{figures/primary-brakes-schematic}
\caption{Schematic of primary braking system}
\label{fig:primary-brakes-schematic}
\end{figure}

@@

\begin{figure}
\centering
%\includegraphics{figures/caliper-mounting-geometry}
\caption{View of dual-primary and parking calipers on front suspension upright }
\label{fig:calipers-mounting-geometry}
\end{figure}

@@

The system uses a collapsible steering column from Sweet Mfg.\@, part number \href{https://sweetmfg.biz/product.php?productid=2836}{405-10310}. The steering system linkage uses multiple U-joints and is shown in Figure \ref{fig:steering-system}.

\begin{figure}
\centering
%\includegraphics{figures/steering-system}
\caption{View of linkage from steering column to rack and pinion}
\label{fig:steering-system}
\end{figure}

@@

\begin{figure}
\centering
%\includegraphics{figures/front-suspension}
\caption{View of front suspension assembly}
\label{fig:front-suspension}
\end{figure}

@@

\begin{figure}
\centering
%\includegraphics{figures/rear-suspension}
\caption{View of rear suspension assembly}
\label{fig:rear-suspension}
\end{figure}

@@

\clearpage
\section{Electrical}

\subsection{Contacts}
Questions regarding the electrical design and implementation of MSXII should be directed to one of the following contacts:

\begin{table}[!h]
\centering
\begin{tabular}{llll}
\toprule
Name        & Title               & Phone        & Email \\
\midrule
Tak Alguire & Project Manager     & 519-574-4610 & tak.alguire@uwmidsun.com \\
Minghao Ji  & Engineering Manager & 519-500-1292 & minghao.ji@uwmidsun.com \\
Titus Chow  & Electrical Lead     & 226-978-7104 & titus.chow@uwmidsun.com \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Overview}
Midnight Sun XII's electrical system consists of high- and low-voltage domains that are electrically isolated for safety. The high-voltage system includes the Sunpower E-series solar cells, Nomura maximum power point trackers, Tritium motor controllers and NGM SCM-150 motors. These are externally-sourced components purchased by the team and interface with the vehicle's custom embedded systems.

@@

Due to the different CAN specifications of the Tritium WaveSculptor motor controllers, they are allocated a separate Powertrain CAN network which interfaces with the primary CAN bus via dedicated transceiver boards. A block diagram of all electrical systems is shown in Figure \ref{fig:msxii-electrical-full-block-diagram}. A block diagram of only the vehicle's high-voltage systems is shown in Figure \ref{fig:msxii-electrical-hv-block-diagram}.

>>>>

\section{Contacts}
Questions regarding the design and implementation of MSXII should be directed to one of the following contacts:

\begin{table}[!h]
\centering
\begin{tabular}{llll}
\toprule
Name            & Title               & Phone        & Email \\
\midrule
Tak Alguire     & Project Manager     & 519-574-4610 & tak.alguire@uwmidsun.com \\
Minghao Ji      & Engineering Manager & 519-500-1292 & minghao.ji@uwmidsun.com \\
Devon Copeland  & Mechanical Lead     & 226-792-7383 & devon.copeland@uwmidsun.com \\
Titus Chow      & Electrical Lead     & 226-978-7104 & titus.chow@uwmidsun.com \\
\bottomrule
\end{tabular}
\end{table}

\section{Mechanical}
\subsection{Overview}
MSXII is a dual-occupant Cruiser class vehicle. Its structural design uses a steel alloy tube chassis with non-structural fibreglass body panels. The majority of the vehicle's powertrain systems are located behind the occupant cell, including the battery pack, power junction box, motor controllers, and EV charger. The vehicle is rear-wheel driven by two hub-mounted DC motors. The locations of these components are marked in Figure \ref{fig:msxii-top-view-annotated} and Figure \ref{fig:msxii-side-view-annotated}. Major vehicle parameters are summarized in Table \ref{tab:msxii-dimensions}.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/msxii-top-view-annotated}
\caption{Top view showing major dimensions and system positions}
\label{fig:msxii-top-view-annotated}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/msxii-side-view-annotated}
\caption{Side view showing major dimensions and system positions}
\label{fig:msxii-side-view-annotated}
\end{figure}

\begin{table}
\centering
\begin{tabular}{cc}
\toprule
Parameter & Value \\
\midrule
Wheelbase    & \SI{2.60}{\metre}    \\
Track        & \SI{1.60}{\metre}    \\
Max length   & \SI{4.68}{\metre}    \\
Max width    & \SI{2.02}{\metre}    \\
Max height   & \SI{1.23}{\metre}    \\
Gross weight & \SI{550}{\kilo\gram} \\
\bottomrule
\end{tabular}
\caption{Table of major vehicle dimensions}
\label{tab:msxii-dimensions}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{figures/chassis-front}
\caption{Chassis, front view}
\label{fig:chassis-front}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/chassis-top}
\caption{Chassis, top view}
\label{fig:chassis-top}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/chassis-side}
\caption{Chassis, side view}
\label{fig:chassis-side}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{figures/welding-jig}
\caption{Welding jig on rotating mount}
\label{fig:welding-jig}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{figures/roll-cage}
\caption{Chassis with roll cage elements highlighted}
\label{fig:roll-cage}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{figures/seat-belt-tab-positions}
\caption{Chassis mounting points for seat belts}
\label{fig:seat-belt-tab-positions}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{figures/seat-belt-tab}
\caption{Single seat belt tab}
\label{fig:seat-belt-tab}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{figures/seat-belt-side-view}
\caption{Side view of seat belt geometry}
\label{fig:seat-belt-side-view}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{figures/seat-belt-top-view}
\caption{Top view of seat belt geometry}
\label{fig:seat-belt-top-view}
\end{figure}

@@

\begin{figure}
\centering
%\includegraphics[width=\textwidth]{figures/primary-brakes-schematic}
\caption{Schematic of primary braking system}
\label{fig:primary-brakes-schematic}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/caliper-mounting-geometry}
\caption{View of dual-primary and parking calipers on front suspension upright }
\label{fig:calipers-mounting-geometry}
\end{figure}

@@

The system uses a collapsible steering column from Sweet Mfg.\@, part number \href{https://sweetmfg.biz/product.php?productid=2836}{405-10310}. The steering system linkage uses multiple U-joints and is shown in Figure \ref{fig:steering-assembly}.

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{figures/steering-assembly}
\caption{View of linkage from steering column to rack and pinion}
\label{fig:steering-assembly}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{figures/front-suspension}
\caption{View of front suspension assembly (parking brake obstructed by hub)}
\label{fig:front-suspension}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{figures/rear-suspension}
\caption{View of rear suspension assembly}
\label{fig:rear-suspension}
\end{figure}

@@

\clearpage
\section{Electrical}
\subsection{Overview}
Midnight Sun XII's electrical system consists of high- and low-voltage domains that are electrically isolated for safety. The high-voltage system includes the Sunpower E-series solar cells, Nomura maximum power point trackers, Tritium motor controllers and NGM SCM-150 motors. These are externally-sourced components purchased by the team and interface with the vehicle's custom embedded systems.

@@

Due to the different CAN specifications of the Tritium WaveSculptor motor controllers, they are allocated a separate powertrain CAN network which interfaces with the primary CAN bus via dedicated transceiver boards. A block diagram of all electrical systems is shown in Figure \ref{fig:msxii-electrical-full-block-diagram}. A block diagram of only the vehicle's high-voltage systems is shown in Figure \ref{fig:msxii-electrical-hv-block-diagram}.
